Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize

### 2017-08-11 R/SubGenome Analysis.Rmd
Implemented a high level GO Term comparison by gene assignment
Accounts for homeolgous genes.

(broken - doesn't take into account homeologous genes - try replacing equivalent genes from homeolog list)

```{r GOTerms_assignments_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% nrow(),
  area2 = goAnnotations.sub2 %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select(gene2, "GO Term"), goAnnotations.sub2 %>% select(gene2, "GO Term")) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term assignments by subgenome (EV-EXP only)")

#EXP only, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select(gene2, "GO Term"), 
                         goAnnotations.sub2 %>% filter(grepl("EV-EXP", EVCode)) %>% select(gene2, "GO Term")
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term assignments by subgenome (EV-EXP only)")
```

>>>>

```{r GOTerms_assignments_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
## Only keep genes where there is a duplicate still on subgenome 1 and subgenome 2
converted <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  right_join(., goAnnotations.sub2,by=c("Maize2"="gene2"))
converted$Maize2[!is.na(converted$Maize1)] <- as.character(converted$Maize1[!is.na(converted$Maize1)])
converted <- 
  converted %>%
  select(Maize2, "GO Term", EVCode) %>%
  rename(gene2=Maize2)

# All EV-Codes, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% nrow(),
  area2 = converted %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% select(gene2, "GO Term") %>% distinct(), 
                         converted %>% select(gene2, "GO Term") %>% distinct()
                         ) %>% nrow(),
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term Assignments by Subgenome\n(EV-EXP only)")

#EXP only, all assignments
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
  area2 = converted %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(grepl("EV-EXP", EVCode)) %>% select(gene2, "GO Term") %>% distinct(), 
                         converted %>% filter(grepl("EV-EXP", EVCode)) %>% select(gene2, "GO Term") %>% distinct()
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term Assignments by Subgenome\n(EV-EXP only)")
```

<!-- ## GO Analysis -> grouping into useful slices -->
<!-- goAnnotations.diff <- -->
<!--   full_join(goAnnotations.sub1.aggr, goAnnotations.sub2.aggr, by="GO Term", is.na=0) %>% -->
<!--   rename(sub1_n=n.x, sub2_n=n.y) %>% -->
<!--   subset(is.na(sub1_n) | is.na(sub2_n)) -->
<!-- goAnnotations.diff.counts <- -->
<!--   full_join(goAnnotations.sub1.aggr, goAnnotations.sub2.aggr, by="GO Term", is.na=0) %>% -->
<!--   rename(sub1_n=n.x, sub2_n=n.y) %>% -->
<!--   replace_na(list(sub1_n=0, sub2_n=0)) %>% -->
<!--   transmute(`GO Term`=`GO Term`,diff=sub1_n-sub2_n) %>% -->
<!--   subset(diff != 0) -->
<!-- goAnnotations.same <- -->
<!--   full_join(goAnnotations.sub1.aggr, goAnnotations.sub2.aggr, by="GO Term") %>% -->
<!--   rename(sub1_n=n.x, sub2_n=n.y) %>% -->
<!--   replace_na(list(sub1_n=0, sub2_n=0)) %>% -->
<!--   transmute(`GO Term`=`GO Term`,diff=sub1_n-sub2_n) %>% -->
<!--   subset(diff == 0) -->

<!-- print("Number of GO terms in sub1 not in sub2") -->
<!-- print(nrow(goAnnotations.diff %>% subset(is.na(sub2_n)))) -->
<!-- print("Number of GO terms in sub2 not in sub1") -->
<!-- print(nrow(goAnnotations.diff %>% subset(is.na(sub1_n)))) -->
